Robust calibration of numerical models based on relative regret

### 2019-11-13 article-modif-A&E.tex
use JCP template

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
%% For further assistance please contact Copernicus Publications at: production@copernicus.org
%% https://publications.copernicus.org/for_authors/manuscript_preparation.html

%% Please use the following documentclass and journal abbreviations for discussion papers and final revised papers.

%% 2-column papers and discussion papers
\documentclass[npg, manuscript]{copernicus}

%% Journal abbreviations (please use the same for discussion papers and final revised papers)

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% ASTRA Proceedings (ap)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% Fossil Record (fr)
% Geographica Helvetica (gh)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)
% Wind Energy Science (wes)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}
\usepackage{easy-todo}
\usepackage{graphicx}

@@

@@

\title{Title-- \today{}}%TEXT}

% \Author[affil]{given_name}{surname}

\Author[]{Victor}{Trappler}
\Author[]{Élise}{Arnaud}
\Author[]{Laurent}{Debreu}
\Author[]{Arthur}{Vidard}

\affil[]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}
% \affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{Title}

\runningauthor{Trappler V.}

\correspondence{Victor Trappler (victor.trappler@univ-grenoble-alpes.fr)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

% \listoftodos\

\begin{abstract}
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
\victor{Pour le nom: Il y a l'idée que l'on veut avoir un regret $J(\mathbf{k},\mathbf{u}) - \alpha J^*(\mathbf{u})$ controlé à l'aide de $\alpha$: Relative regret ?}
\end{abstract}

\copyrightstatement{TEXT}

@@

\begin{table*}[t]
  \caption{Robust estimators, based on a cost function $J$}
  \label{tab:RO_recap}
\begin{tabular}{lrr}
  \tophline
  Definition & Related quantities & Interpretation \\
  \middlehline
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \bottomhline
\end{tabular}
\end{table*}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\tophline
Estimate & Value \\ \middlehline
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\hatkmpe$ & 1.628 \\ 
$\kest_p,~p=0.95$ & 1.672 \\ 
$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \bottomhline
\end{tabular}
\end{table*}

@@

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \tophline
Estimate & Value \\ \middlehline
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\kest_{\mathrm{mean}}$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\kest_{\mathrm{var}}$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomhline
\end{tabular}
\end{table*}

@@

The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient. The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1$. The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.

\begin{align}
  \label{eq:SWE_equations}
  \left\{
    \begin{array}{rl}
      \partial_t h + \partial_x q &= 0 \\
      \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(2 \pi t\right)\\
      \partial_x q(0, t) &= 0
      \end{array}
  \right.
\end{align}
These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$. The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u})$.
In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}})$. 
This true value $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
\begin{equation*}
{k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
\end{equation*}
where $x_i$ is the center of the $i$-th volume.
\subsection{Estimation}

\begin{figure}[!h]
\centering
\includegraphics[width=12cm]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:my_label}
\end{figure}
\begin{table*}[!h]
\centering
\begin{tabular}{lr}
Estimator & Value \\ \hline
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hat{\mathbf{k}}_{\mathrm{mean}}$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hat{\mathbf{k}}_{\mathrm{var}}$ & 0.990 \\
\end{tabular}
\caption{Estimation of $\mathbf{k}$ according to different criterion}
\label{tab:recap_estimates_metaSWE}
\end{table*}

\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed on the time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts depending on the criterion used to calibrate the bottom friction.
To define those forecasts, the models will be integrated from $T$ to $T_{\mathrm{pred}}$.

Given the probabilistic nature $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.

\subsubsection{Squared forecast error}
Let us assume that the observations result from the parameter $\mathbf{u}'$, while the computer simulation is run using $\mathbf{u}$.
The squared forecast error given $\mathbf{u}$ and $\mathbf{u}'$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
We can then get an estimation of the mean squared forecast per volume per time step:

\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'}\left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}

\subsubsection{Averaged Quantile score}
A first approach is to compare the quantiles obtained by the prediction $\mathcal{M}_{\mathrm{pred}}(\kest,\mathbf{U})$, with the quantiles observed of $\mathcal{M}^o_{\mathrm{pred}}(\mathbf{U})$.
We are first going to introduce the pinball loss, or checkloss function:
\begin{equation}
\label{eq:checkloss}
\rho_{\tau}(x) = \begin{cases}
    \tau |x| \quad \text{ if } x \geq 0 \\
    (1- \tau) |x| \quad \text{ if } x < 0
\end{cases}
\end{equation}

Given the time index $j$, and the volume indexed by $i$, the quantile of order $\tau\in [0, 1]$ of $\mathcal{M}(\kest, \mathbf{U})_{(i,j)}$ is $q_{(i,j)}(\tau)$.
Given an obse
\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/forecast_metric.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figures show}
\label{fig:forecast_metric}
\end{figure*}

% \subsection{The Lorenz-63 model}
% A classical toy problem in data assimilation is the Lorenz-63 model, introduced in \cite{lorenz_deterministic_1963}. 
% % xb
% The evolution of the state vector $(x,y,z)$ is described by the non-linear differential system of Eq.~\eqref{eq:lorenz_equations}
% \begin{align}
%   \label{eq:lorenz_equations}
%   \left\{
%     \begin{array}{l}
%       \dot{x} = \sigma\left(y-x \right) \\
%       \dot{y} = \rho x - y - xz \\
%       \dot{z} = xy - \beta z
%       \end{array}
%   \right.
% \end{align}
% Despite its apparent simplicity, this system is known to show chaotic behaviour for $(\sigma,\rho,\beta) = (10, 28, 8/3)$. 
% This differential system is solved numerically using a Runge-Kutta scheme, over $N=100$ time-steps of length $\Delta t = 0.05$. In that time-period, the chaotic behaviour is not yet too apparent.

% The inputs of the computer code are the initial conditions $\left(x_0,y_0,z_0\right)$ and $(\sigma, \beta, \rho)$. The parameter to calibrate is $\mathbf{k}=x_0-1$ with $\mathbf{k}\in[-0.05,0.05]$, and the uncertain parameter is $\mathbf{u}=\beta - 8/3$ with $\mathbf{u} \in \Uspace=[-0.05, 0.05]$. Finally, we suppose that the random variable $\mathbf{U}$ follows an uniform distribution on $\Uspace$. Solving numerically the differential system using those settings yields $x_{i}(\mathbf{k},\mathbf{u})$ for $i$ between $1$ and $N$.

% This problem of calibration will be studied in a twin experiments framework: the target state $x^{o}_i$ for $1\leq i \leq N$ has been generated by the computer code, where the parameters used to generate it are detailed in Table~\ref{tab:lorenz_modelling}. One can notice the discrepancy of $\rho$ between the observations and the model, introduced to ensure that no perfect fit can be achieved, for any set of parameters. 
% \begin{table*}[h]
%   \caption{Choice of modelling of the Lorenz-63 system}
%   \label{tab:lorenz_modelling}
% \begin{tabular}{crrl}
%   \tophline
%   Parameter & Observation: $x_{1:N}^o$ & Modelling: $\mathcal{G}(\mathbf{k},\mathbf{u})$ & Type \\
%   \middlehline
%  $\sigma$ & $10$ & $10$ & Fixed\\
%   $\rho$ & $29$ & $28$ & A priori chosen and fixed \\
%   $\beta$ & ${8}/{3}$ & ${8}/{3} + \mathbf{u}$ & A priori chosen and uncertain \\
%  $x_0$ & $1$ & $1 + \mathbf{k}$ & Calibrated \\
%   $y_0$ & $0$ & $0$ & Fixed \\
%  $z_0$ & $0$ & $0$ & Fixed \\
%   \bottomhline
% \end{tabular}
% \end{table*}

% The misfit between the observations and the output of the numerical model is quantified using the cost function:
% \begin{equation}
% \label{eq:cost_fun_lorenz}
% J(\mathbf{k},\mathbf{u}) = \frac{1}{2}\|\mathcal{G}(\mathbf{k},\mathbf{u}) \|^2 = \frac{1}{2} \|x_{1:N}(\mathbf{k},\mathbf{u}) - x^o_{1:N} \|^2 = \frac{1}{2}\sum_{i=1}^N (x_i(\mathbf{k},\mathbf{u}) - x_i^o)^2
% \end{equation}

% This toy model is cheap to evaluate, so the global minimum can be computed using numerical methods, at different starting points to avoid local minimums.
% \begin{equation}
% \label{eq:min_global_lorenz}
% \min_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = 38.886712815 \quad \argmin_{(\mathbf{k},\mathbf{u}) \in \Kspace\times\Uspace} J(\mathbf{k},\mathbf{u}) = (0.02414384, -0.00551042)
% \end{equation}

% \subsubsection{MPE and conditional moments}
% Figure~\ref{fig:lorenz_kde_moments} shows the cost function $J$, computed on a regular grid over $\Kspace\times\Uspace$. Using this grid, the conditional mean and standard deviation have been computed, while the MPE has been estimated by KDE. For a single $\mathbf{u}$, it may appear that there are multiple $\mathbf{k}^*(\mathbf{u})$. This is due to the fact that the conditional minimiser jumps back and forth between the two curves.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_kde_moments.pdf}
% \caption{Cost function, locus of conditional minimisers, MPE estimated with KDE, conditional moments and their associated estimates}
% \label{fig:lorenz_kde_moments}
% \end{figure}

% \subsubsection{Relaxation of the constraint}
% Based on the computations described before, the coefficient $\checkap$ have been computed for $p=0.9$, $0.95$ and $p=1$, and reported in Table~\ref{tab:recap_estimates_lorenz}. The curve $R_{\checka_1}$ is plotted in Figure~\ref{fig:lorenz_relax}, where the acceptable region for $\checka_1$ is filled in yellow.

% \begin{figure}[!h]
% \includegraphics[width=12cm]{Figures/lorenz_f3.pdf}
% \caption{Relaxation of the constraint for the Lorenz model. Acceptable region in yellow}
% \label{fig:lorenz_relax}
% \end{figure}

% We can see that for $\mathbf{k}$ being approximately between $0$ and $0.01$, the probability $R_{\checka_1}$ is very close to $1$. Indeed, the cost function seems to be relatively flat on this region, as $\checkk_{0.9} \approx \kmpe$.

>>>>

%% 
%% Copyright 2007-2019 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% l
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint, 1p]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\usepackage{easy-todo}
\usepackage{graphicx}

@@

\journal{Journal of Computational Physics}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:

\title{Robust calibration of numerical models based on relative regret}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[vt]{Victor Trappler}
\ead{victor.trappler@univ-grenoble-alpes.fr}
\author[ea]{Élise Arnaud}
\author[av]{Arthur Vidard}
\author[ld]{Laurent Debreu}

\address[vt]{Univ. Grenoble Alpes, CNRS, Inria, Grenoble INP*, LJK, 38000 Grenoble, France}

\begin{abstract}
%% Text of abstract
Classical methods of parameter estimation usually imply the minimisation of an objective function, that measures the error between some observations and the results obtained by a numerical model. In the presence of random inputs, the objective function becomes a random variable, and notions of robustness have to be introduced.

In this paper, we are going to present how to take into account those uncertainties by defining a notion of robustness based on the distribution of the conditional minimisers and compare it with the minimum in the mean sense, and the minimum of variance.
\end{abstract}

% %%Graphical abstract
% \begin{graphicalabstract}
% %\includegraphics{grabs}
% \end{graphicalabstract}

%%Research highlights
% \begin{highlights}
% \item Research highlight 1
% \item Research highlight 2
% \end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section*{Introduction}
\label{}

@@

\begin{table*}[t]
  \caption{Robust estimators, based on a cost function $J$}
  \label{tab:RO_recap}
\begin{tabular}{lrr}
  \hline
  Definition & Related quantities & Interpretation \\
  \hline
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \hline
\end{tabular}
\end{table*}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\hline
Estimate & Value \\ \hline
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\hatkmpe$ & 1.628 \\ 
$\kest_p,~p=0.95$ & 1.672 \\ 
$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \hline
\end{tabular}
\end{table*}

@@

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \hline
Estimate & Value \\ \hline
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\kest_{\mathrm{mean}}$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\kest_{\mathrm{var}}$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \hline
\end{tabular}
\end{table*}

@@

The model we wish to calibrate is based on the Shallow Water equations, described Eq.~\eqref{eq:SWE_equations}. $h$ is the height of the water column, $q$ is the discharge, and $z$ is the bathymetry, while $g$ is the usual gravitation constant. The parameter to calibrate, $\mathbf{k}$, is the quadratic friction term, proportional to the square of the inverse of Manning-Strickler coefficient. The environmental parameter $\mathbf{u}$ is the amplitude of a sine wave of period $1/\omega_0$. The domain of those two parameters are $\mathcal{K} = [0.0, 1.3]$ and $\mathcal{U} = [0.5, 0.7]$.

\begin{align}
  \label{eq:SWE_equations}
  \left\{
    \begin{array}{rl}
      \partial_t h + \partial_x q &= 0 \\
      \partial_t q + \partial_x \left(\frac{q^2}{h} + \frac{g}{2}h^2\right) &= - gh\partial_x z - \mathbf{k}q |q|h^{-7/3} \\
      h(0, t) &= 20.0 + 3\cdot \sin \left(\frac{2\pi t}{2}\right) + 1.5\cdot \mathbf{u} \cdot \sin\left(\frac{2 \pi t}{\omega_0}\right)\\
      \partial_x q(0, t) &= 0
      \end{array}
  \right.
\end{align}
These equations are integrated using a finite-volume scheme on a discretized domain $[0, L]$, up to a time $T$. The output of the computer code is the sea surface height $h$, on the center of all the volumes and at all the time-steps, that will be denoted $\mathcal{M}(\mathbf{k},\mathbf{u};\, \omega_0=1.0)$.
In this setting, the variable input is uniformly distributed on $\mathcal{U}$.
To generate the observations, we choose $\mathbf{u}^{\mathrm{true}}=2/3$, and define $\mathcal{M}^o$ based on the computer model $\mathcal{M}$, such that $\mathcal{M}^o(\mathbf{u}^{\mathrm{true}}) = \mathcal{M}(\mathbf{k}^{\mathrm{true}}, \mathbf{u}^{\mathrm{true}}; \, \omega_0 = 0.999)$. $\omega_0$  
represents here the uncontrollable error between the observations and the numerical model and will now be omitted systematically in the notation. The true value of the bottom friction $\mathbf{k}^{\mathrm{true}} = (k_1^{\mathrm{true}}, k_2^{\mathrm{true}},\dots, k_{N_\mathrm{vol}}^{\mathrm{true}})$ is not constant over the whole domain, and is defined as
\begin{equation*}
{k}^{\mathrm{true}}_i = 0.2\cdot \left(1 + \sin\left(\frac{2 \pi x_i}{L}\right)\right)
\end{equation*}
where $x_i$ is the center of the $i$-th volume. The two sources of representativity errors are $\omega_0$, and the fact that we are looking to estimate $\mathbf{k}$ in a 1-dimensional space $\Kspace$. 
\subsection{Estimation}
Given that the numerical model is expensive to evaluate, it has first been evaluated on a relatively small regular grid. A metamodel based on Gaussian process is constructed and the PEI criterion \citep{ginsbourger_bayesian_2014,bossek_learning_2015} allow us to add point to evaluate and to better capture the locus of the conditional minimisers $\{(\mathbf{k}^*(\mathbf{u}), \mathbf{u}) \mid \mathbf{u} \in \Uspace \}$. A bigger regular grid is evaluated by the metamodel once the design space has been sufficiently explored. The different steps of the estimation are illustrated Figure~\ref{fig:estimation_swe}. We can see that the estimation for this problem seems less problematic than the analytical examples shown above, as all derived quantites are unimodal.
The different estimates however take a wide range of values, as seen on Table~\ref{tab:recap_estimates_metaSWE}.: there is a unique global minimiser on the whole space $\Kspace \times \Uspace$, noted $\kest_{\mathrm{global}}$. As discussed earlier, the estimation of the MPE is dependent on the method used, and then its estimation using KDE in the middle plot of Figure~\ref{fig:estimation_swe} is here only for illustrative purposes.

\begin{figure}[!h]
\centering
\includegraphics[width=12cm]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \hline
Estimator & Value \\ \hline
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \hline
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}

\subsection{Assessing the quality of the forecast of the calibrated model}
The calibration of the model has been performed using by integrating the model on a time-period $[0, T]$, called assimilation window. 
We now want to compare the quality of the different forecasts, from different calibrated bottom friction.
Those forecasts result from the integration of the numerical model between the time $T$ and a time $T_{\mathrm{pred}}$.

Given the probabilistic nature of the environmental conditions $\mathbf{U}$, the forecasts will also be probabilistic. We will then compare $\mathcal{M}_{\mathrm{pred}}^o(\mathbf{U})$ and $\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{U})$, for a calibrated $\mathbf{k}$.

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
By averaging over $\mathbf{u}$ and $\mathbf{u}'$ using a Monte-Carlo approximation, we can define the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
The mean squared forecast error is then averaged over all time-steps between $T$ and $T_{\mathrm{pred}}$, indicating on which point of the domain the forecast error is greater as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=12cm]{Figures/forecast_error.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.

Figure~\ref{fig:forecast_squared_error_distrib} shows the distribution of the mean squared error. 
\begin{figure*}[!h]
\centering
\includegraphics[width=10cm]{Figures/forecast_error_distrib_2.pdf}
\caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
\label{fig:forecast_squared_error_distrib}
\end{figure*}

\subsubsection{Continuous Ranked Probability Score}
The Continuous ranked probability score (CRPS) measure the squared difference between the predicted CDF $F_{\mathrm{pred}}$ using a calibrated value, and the CDF of the observation $F_{\mathrm{pred}}^o$. 
\begin{equation}
\label{eq:def_crps}
\mathrm{CRPS}(\mathbf{k}) = \int_{\mathbb{R}} (F_{\mathrm{pred}}(x,\mathbf{k}) - F^o_{\mathrm{pred}}(x))^2 \,\mathrm{d}x
\end{equation}

\clearpage
\section*{Conclusion}  %% \conclusions[modified heading if necessary]
This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.
